An Algorithm For Spatial Mapping Using a Hexagon Tilegram, With Application to Australian Maps

### 2019-07-30 algorithmRjournal/algorithmRjournal.Rmd
Hide table code

**The following must be provided to `create_hexmap`:**
```{r table_necessary}
knitr::kable(tibble::tibble(parameter = c('shp', 
  'sf_id',
  'focal_points'),
  description = c(
    'an sf object containing the polygon information', 
    'name of a column that distinguishes unique areas',
    'a data frame of reference locations used to allocate hexagons'
    )), format = "latex")
```

@@

```{r parameters}
knitr::kable(tibble(parameter = c('buffer_dist', 'hex_size',  'hex_filter', 'width'),
  description = c('a float value for distance in degrees to extend beyond the geometry provided',
    'a float value in degrees for the diameter of the hexagons', 'amount of hexagons around centroid to consider for allocation',
    'the angle used to filter the grid points around a centroid')), format = "latex")
```

>>>>

**The following must be provided to `create_hexmap`:**
```{r table_necessary, echo = FALSE}
knitr::kable(tibble::tibble(parameter = c('shp', 
  'sf_id',
  'focal_points'),
  description = c(
    'an sf object containing the polygon information', 
    'name of a column that distinguishes unique areas',
    'a data frame of reference locations used to allocate hexagons'
    )), format = "latex")
```

@@

```{r parameters, echo = FALSE}
knitr::kable(tibble(parameter = c('buffer_dist', 'hex_size',  'hex_filter', 'width'),
  description = c('a float value for distance in degrees to extend beyond the geometry provided',
    'a float value in degrees for the diameter of the hexagons', 'amount of hexagons around centroid to consider for allocation',
    'the angle used to filter the grid points around a centroid')), format = "latex")
```

### 2019-07-30 algorithmRjournal/algorithmRjournal.tex
Hide table code

\begin{Schunk}
\begin{Sinput}
knitr::kable(tibble::tibble(parameter = c('shp', 
  'sf_id',
  'focal_points'),
  description = c(
    'an sf object containing the polygon information', 
    'name of a column that distinguishes unique areas',
    'a data frame of reference locations used to allocate hexagons'
    )), format = "latex")
\end{Sinput}

@@

\textbf{The following parameters will be determined within
\texttt{create\_hexmap} if not provided. They are created throughout the
following example:}

\begin{Schunk}
\begin{Sinput}
knitr::kable(tibble(parameter = c('buffer_dist', 'hex_size',  'hex_filter', 'width'),
  description = c('a float value for distance in degrees to extend beyond the geometry provided',
    'a float value in degrees for the diameter of the hexagons', 'amount of hexagons around centroid to consider for allocation',
    'the angle used to filter the grid points around a centroid')), format = "latex")
\end{Sinput}

@@

\hypertarget{hexagon-grid}{%
\subsection{Hexagon grid}\label{hexagon-grid}}

@@

\hypertarget{allocation-of-centroids}{%
\subsection{Allocation of centroids}\label{allocation-of-centroids}}

>>>>

@@

\textbf{The following parameters will be determined within
\texttt{create\_hexmap} if they are not provided. They are created
throughout the following example:}

@@

\hypertarget{create-the-hexagon-grid-points}{%
\subsection{Create the hexagon grid
points}\label{create-the-hexagon-grid-points}}

@@

\hypertarget{allocate-each-centroids-to-a-hexagon-grid-point}{%
\subsection{Allocate each centroids to a hexagon grid
point}\label{allocate-each-centroids-to-a-hexagon-grid-point}}
